Numerical trajectory patterns of floating macroalgae

### 2020-11-04 thesis_chapter_3.Rmd
added surface area table
update

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  html_document:
  pdf_document:
    fig_caption: yes
  word_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  pdf_document:
    fig_caption: yes
  html_document:
  word_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table
```
